Methods for Large Scale Learning to Rank

### 2014-04-03 report/Chapters/CrossBenchmarkComparison.tex
tabel

\section{Evaluation Results Found in Literature}

@@

\subsection{All metrics}
\begin{figure}[!h]
\includegraphics[scale=0.40]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?$
%TODO: limitations van deze vergelijkingsmethodologie$

>>>>

\section{Evaluation Results Found in Literature}
\begin{tabular}{llll}
AdaRank-\ac{MAP} & FenchelRank & LambdaRank & RankDE \\ 
AdaRank-\ac{nDCG} & FocusedBoost & LARF & Ranking Committee Perceptron \\ 
ADMM & FocusedNet & ListMLE & RankMGP \\ 
Approx\ac{AP} & FocusedSVM & ListNet & RankNet \\ 
Approx\ac{nDCG} & FPRank & ListReg & RankRLS \\ 
BagBoo & FRank & LRUF & RankSVM \\ 
Best Single Feature & FSMRank & MBP & RankSVM-Primal \\ 
BL-MART & FSM$^{MAP}$ & MHR & RankSVM-Struct \\ 
BoltzRank-Single & GAS-E & MultiStageBoost & RE-QR \\ 
BoltzRank-Pair & GPRank & NewLoss & REG-SHF-SDCG \\ 
BT & GRankRLS & OWPC & Regression \\ 
C-CRF & GroupCE & RankELM (pointwise) & RSRank \\ 
CA & GroupMLE & RankELM (pairwise) & SmoothGrad \\ 
 &  & TM & VFLR \\ 
CCRank & IntervalRank & PERF-MAP & SmoothRank \\ 
CoList & KeepRank & PermuRank & SoftRank \\ 
Consistent-RankCosine & Kernel-PCA & Q.D.KNN & SortNet \\ 
CRR & KL-CRF & RandomForest & SparseRank \\ 
DCMP & Regression with L2-regularisation & Rank-PMBGP & SVD-RankBoost \\ 
DirectRank & LAC-MR-OR & RankAgg\ac{nDCG} & SVM$^{MAP}$ \\ 
Energy\ac{nDCG} & LambdaMART & RankBoost & SwarmRank \\ 
FBPCRank & LambdaNeuralRank & RankCSA & TGRank \\ 
\end{tabular}

@@

\subsection{All metrics}
\begin{figure}[!h]
\includegraphics[scale=0.40]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?
%TODO: limitations van deze vergelijkingsmethodologie
